---
title: "Demonstration of pipeLIMMA"
author: "JT Lovell"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The R package limmaDE2 contains a set of functions designed to make running differential expression analyses in LIMMA more user friendly. There are several functions of this package:

- `pipeLIMMA` Run analyses of differnetial expression ()
- `makeBinarySig` Find and count the number of significantly differentially expressed genes
- `pqHists` Plot the distribution of P and FDR-corrected P (Q) values
- `voom2PCA` Conduct principal component analyses on voom (or otherwise) normalized expression matrices
- `volcanoPlot` Generate log2 foldchange vs. P-value volcano plots
- `volcanoPair` Compare two sets of log2 fold changes, colored by p-values


## Installation
The limmaDE2 packages is not on CRAN and can only be installed from github. To install the package, make sure the `devtools` package is installed on your system:

```{r}
library(devtools)

```


Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
